Manuscript

### 2018-11-27 manuscript.Rmd
manuscript plots/data update

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_withGroupedLineages.csv", sep = "\t", header = TRUE, row.names = 1)
g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
g2p$Drug <- tolower(g2p$Drug)
g2p[g2p == -1] <- NA
g2p$Ref[g2p$Ref == "None"] <- NA
g2p$Alt[g2p$Alt == "None"] <- NA
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))

g2p_drug_genes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

```{r, eval=FALSE}
maf_df <- readRDS("./data_munging/rds/maf_df_18Q4.rds")
cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q4.rds")
ge_melt_18Q3 <- readRDS("./../htscreen_lineages_giant_files/ge_melt_18Q3.rds")
# ge_melt_18Q4 <- readRDS("./data_munging/rds/ge_melt_18Q4.rds")
```

@@

@@

```{r fig.height=15, fig.width=15, eval=FALSE}
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = as.character(unique((crispr_signif_g2p_lineage$Hugo_Symbol)))

@@

crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES score by cell line lineage for significant Level A G2P genes",
       subtitle = "* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
crispr_data_signif_g2p_lineage_plot

# ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
```

@@

G2P summary stats:
```{r}
g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
range(g2p_druggene_p_tally$n)
mean(g2p_druggene_p_tally$n)
sd(g2p_druggene_p_tally$n)

g2p_drug_tally <- g2p %>% group_by(Drug) %>% tally() %>% drop_na()
range(g2p_drug_tally$n)
mean(g2p_drug_tally$n)
sd(g2p_drug_tally$n)

g2p_gene_tally <- g2p %>% group_by(Gene) %>% tally() %>% drop_na()
range(g2p_gene_tally$n)
mean(g2p_gene_tally$n)
sd(g2p_gene_tally$n)
```

@@

```{r}
ccle_druggene_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ccle_druggene_summ$n <- ifelse(is.na(ccle_druggene_summ$n), 0, ccle_druggene_summ$n)
ccle_druggene_summ$InG2P <- ifelse(ccle_druggene_summ$n != 0, "Yes", "No")
ccle_druggene_summ$Dataset <- "CCLE"
ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 1), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 3))

ctrp_druggene_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ctrp_druggene_summ$n <- ifelse(is.na(ctrp_druggene_summ$n), 0, ctrp_druggene_summ$n)
ctrp_druggene_summ$InG2P <- ifelse(ctrp_druggene_summ$n != 0, "Yes", "No")
ctrp_druggene_summ$Dataset <- "CTRP"
ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 1), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", round(ctrp_p_ttest$p.value, 3))

gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
gdsc_druggene_summ$Dataset <- "GDSC"
gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 1), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", round(gdsc_p_ttest$p.value, 3))

@@

ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

@@

```{r}
ccle_pearson_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
ccle_pearson_res <- merge(g2p_druggene_p_tally, ccle_pearson_res, by = "Drug_Gene", all.y = TRUE)
ccle_pearson_res$n <- ifelse(is.na(ccle_pearson_res$n), 0, ccle_pearson_res$n)
ccle_pearson_res$InG2P <- ifelse(ccle_pearson_res$n != 0, "Yes", "No")
ccle_pearson_res$Dataset <- "CCLE"
ccle_pearson_ttest_GE <- t.test(ccle_pearson_res$Pearson_Corr_GE ~ ccle_pearson_res$InG2P)
ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 1), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 3))
ccle_pearson_ttest_CN <- t.test(ccle_pearson_res$Pearson_Corr_CN ~ ccle_pearson_res$InG2P)
ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 1), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 3))

ctrp_pearson_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
ctrp_pearson_res <- merge(g2p_druggene_p_tally, ctrp_pearson_res, by = "Drug_Gene", all.y = TRUE)
ctrp_pearson_res$n <- ifelse(is.na(ctrp_pearson_res$n), 0, ctrp_pearson_res$n)
ctrp_pearson_res$InG2P <- ifelse(ctrp_pearson_res$n != 0, "Yes", "No")
ctrp_pearson_res$Dataset <- "CTRP"
ctrp_pearson_ttest_GE <- t.test(ctrp_pearson_res$Pearson_Corr_GE ~ ctrp_pearson_res$InG2P)
ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 1), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p = ", round(ctrp_pearson_ttest_GE$p.value, 3))
ctrp_pearson_ttest_CN <- t.test(ctrp_pearson_res$Pearson_Corr_CN ~ ctrp_pearson_res$InG2P)
ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 1), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))

gdsc_pearson_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
gdsc_pearson_res <- merge(g2p_druggene_p_tally, gdsc_pearson_res, by = "Drug_Gene", all.y = TRUE)
gdsc_pearson_res$n <- ifelse(is.na(gdsc_pearson_res$n), 0, gdsc_pearson_res$n)
gdsc_pearson_res$InG2P <- ifelse(gdsc_pearson_res$n != 0, "Yes", "No")
gdsc_pearson_res$Dataset <- "GDSC"
gdsc_pearson_ttest_GE <- t.test(gdsc_pearson_res$Pearson_Corr_GE ~ gdsc_pearson_res$InG2P)
gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 1), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
gdsc_pearson_ttest_CN <- t.test(gdsc_pearson_res$Pearson_Corr_CN ~ gdsc_pearson_res$InG2P)
gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 1), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))

@@

ggsave("./plots/manuscript/g2p_druggene_ge_plot.png", g2p_druggene_ge_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

@@

Mutation status summary stats:
```{r}
g2p_druggene_all_summ_stats <- g2p_druggene_all_summ
g2p_druggene_all_summ_stats$n_true <- TRUE
g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 3), p_sd = round(sd(p), 3), n = sum(n_true), n_signif = sum(p < 0.05))
```

Pearson summary stats:
```{r fig.height=4, fig.width=5}
g2p_druggene_pearson_stats <- g2p_druggene_pearson
g2p_druggene_pearson_stats$n_true <- TRUE
g2p_druggene_pearson_stats <- g2p_druggene_pearson_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(ge_mean = round(mean(Pearson_GE_Abs), 3),
          ge_sd = round(sd(Pearson_GE_Abs), 3),
          ge_n = sum(n_true),
          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
          cn_mean = round(mean(Pearson_CN_Abs), 3),
          cn_sd = round(sd(Pearson_CN_Abs), 3),
          cn_n = sum(n_true),
          cn_n_signif = sum(Pearson_Pval_CN < 0.05))

@@

ctrp_grid_summary_mut_corr <- wilcox.test(AUC_zscore ~ Mutation_Status_Nonsilent, data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], paired = FALSE)
ctrp_grid_summary_mut_corr_text <- paste0("W = ", ctrp_grid_summary_mut_corr$statistic, ", p = ", round(ctrp_grid_summary_mut_corr$p.value, 3))

ctrp_grid_summary_ge_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$RPKM, method = "pearson", use = "complete.obs")
ctrp_grid_summary_ge_corr_text <- paste0("r = ", round(ctrp_grid_summary_ge_corr$estimate, 3), ", t(", ctrp_grid_summary_ge_corr$parameter, ") = ", round(ctrp_grid_summary_ge_corr$statistic, 2), ", p = ", round(ctrp_grid_summary_ge_corr$p.value, 3))

ctrp_grid_summary_cn_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$CN, method = "pearson", use = "complete.obs")
ctrp_grid_summary_cn_corr_text <- paste0("r = ", round(ctrp_grid_summary_cn_corr$estimate, 3), ", t(", ctrp_grid_summary_cn_corr$parameter, ") = ", round(ctrp_grid_summary_cn_corr$statistic, 2), ", p = ", round(ctrp_grid_summary_cn_corr$p.value, 3))

ctrp_grid_summary_mut_plot <- ggplot(data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], aes(y = AUC_zscore, x = Mutation_Status_Nonsilent, fill = Mutation_Status_Nonsilent)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.6) +
  geom_jitter(width = 0.2, shape = 21) +
  scale_fill_manual(values = c("Wildtype" = "lightsteelblue1", "Mutant" = "steelblue4")) +
  annotate(geom = "text", label = ctrp_grid_summary_mut_corr_text, x = 1.5, y = 1.3) +
  guides(fill = FALSE) +
  labs(x = "ERBB2 mutation status", y = "Afatinib AUC (z-score)")
ctrp_grid_summary_mut_plot

>>>>

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_NOV_27.csv", sep = "\t", header = TRUE)
# g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
g2p$Drug <- tolower(g2p$Drug)
g2p[g2p == -1] <- NA
g2p$Ref[g2p$Ref == "None"] <- NA
g2p$Alt[g2p$Alt == "None"] <- NA
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))

g2p_drug_genes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
g2p_drug_genes
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

@@

```{r, eval=FALSE}
maf_df <- readRDS("./data_munging/rds/maf_df_18Q4.rds")
cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q4.rds")
ge_melt_18Q3 <- readRDS("./../htscreen_lineages_giant_files/ge_melt_18Q3.rds")
# ge_melt_18Q4 <- readRDS("./data_munging/rds/ge_melt_18Q4.rds")

# maf_filt_dan <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
# write.table(maf_filt_dan, file = "~/Desktop/maf_filt_dan_18Q4_2018112.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r}
test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()

```

@@

```{r fig.height=18, fig.width=15, eval=TRUE}
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = as.character(unique((crispr_signif_g2p_lineage$Hugo_Symbol))))

@@

crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
  facet_wrap(~ Hugo_Symbol, nrow = 6, scales = "free_y") +
  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES score by cell line lineage for significant Level A G2P genes",
       subtitle = "* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
crispr_data_signif_g2p_lineage_plot

# ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 15, height = 18, units = "in")
```

@@

G2P summary stats:
```{r}
g2p_druggene_p_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
range(g2p_druggene_p_tally$n)
mean(g2p_druggene_p_tally$n)
sd(g2p_druggene_p_tally$n)

g2p_drug_tally <- g2p_filt %>% group_by(Drug) %>% tally() %>% drop_na()
range(g2p_drug_tally$n)
mean(g2p_drug_tally$n)
sd(g2p_drug_tally$n)

g2p_gene_tally <- g2p_filt %>% group_by(Gene) %>% tally() %>% drop_na()
range(g2p_gene_tally$n)
mean(g2p_gene_tally$n)
sd(g2p_gene_tally$n)
```

@@

```{r}
ccle_druggene_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ccle_druggene_summ$n <- ifelse(is.na(ccle_druggene_summ$n), 0, ccle_druggene_summ$n)
ccle_druggene_summ$InG2P <- ifelse(ccle_druggene_summ$n != 0, "Yes", "No")
ccle_druggene_summ$Dataset <- "CCLE"
ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 0), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 2))

ctrp_druggene_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ctrp_druggene_summ$n <- ifelse(is.na(ctrp_druggene_summ$n), 0, ctrp_druggene_summ$n)
ctrp_druggene_summ$InG2P <- ifelse(ctrp_druggene_summ$n != 0, "Yes", "No")
ctrp_druggene_summ$Dataset <- "CTRP"
ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))

gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
gdsc_druggene_summ$Dataset <- "GDSC"
gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", round(gdsc_p_ttest$p.value, 2))

@@

# ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

@@

```{r}
ccle_pearson_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
ccle_pearson_res <- merge(g2p_druggene_p_tally, ccle_pearson_res, by = "Drug_Gene", all.y = TRUE)
ccle_pearson_res$n <- ifelse(is.na(ccle_pearson_res$n), 0, ccle_pearson_res$n)
ccle_pearson_res$InG2P <- ifelse(ccle_pearson_res$n != 0, "Yes", "No")
ccle_pearson_res$Dataset <- "CCLE"
ccle_pearson_ttest_GE <- t.test(ccle_pearson_res$Pearson_Corr_GE ~ ccle_pearson_res$InG2P)
ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
ccle_pearson_ttest_CN <- t.test(ccle_pearson_res$Pearson_Corr_CN ~ ccle_pearson_res$InG2P)
ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))

ctrp_pearson_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
ctrp_pearson_res <- merge(g2p_druggene_p_tally, ctrp_pearson_res, by = "Drug_Gene", all.y = TRUE)
ctrp_pearson_res$n <- ifelse(is.na(ctrp_pearson_res$n), 0, ctrp_pearson_res$n)
ctrp_pearson_res$InG2P <- ifelse(ctrp_pearson_res$n != 0, "Yes", "No")
ctrp_pearson_res$Dataset <- "CTRP"
ctrp_pearson_ttest_GE <- t.test(ctrp_pearson_res$Pearson_Corr_GE ~ ctrp_pearson_res$InG2P)
ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
ctrp_pearson_ttest_CN <- t.test(ctrp_pearson_res$Pearson_Corr_CN ~ ctrp_pearson_res$InG2P)
ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))

gdsc_pearson_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
gdsc_pearson_res <- merge(g2p_druggene_p_tally, gdsc_pearson_res, by = "Drug_Gene", all.y = TRUE)
gdsc_pearson_res$n <- ifelse(is.na(gdsc_pearson_res$n), 0, gdsc_pearson_res$n)
gdsc_pearson_res$InG2P <- ifelse(gdsc_pearson_res$n != 0, "Yes", "No")
gdsc_pearson_res$Dataset <- "GDSC"
gdsc_pearson_ttest_GE <- t.test(gdsc_pearson_res$Pearson_Corr_GE ~ gdsc_pearson_res$InG2P)
gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
gdsc_pearson_ttest_CN <- t.test(gdsc_pearson_res$Pearson_Corr_CN ~ gdsc_pearson_res$InG2P)
gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))

@@

# ggsave("./plots/manuscript/g2p_druggene_ge_plot.png", g2p_druggene_ge_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

@@

Mutation status summary stats:
```{r}
g2p_druggene_all_summ_stats <- g2p_druggene_all_summ
g2p_druggene_all_summ_stats$n_true <- TRUE
g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05))
```

Pearson summary stats:
```{r fig.height=4, fig.width=5}
g2p_druggene_pearson_stats <- g2p_druggene_pearson
g2p_druggene_pearson_stats$n_true <- TRUE
g2p_druggene_pearson_stats <- g2p_druggene_pearson_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
          ge_mean = round(mean(Pearson_GE_Abs), 5),
          ge_sd = round(sd(Pearson_GE_Abs), 5),
          ge_n = sum(n_true),
          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
          cn_mean = round(mean(Pearson_CN_Abs), 3),
          cn_sd = round(sd(Pearson_CN_Abs), 5),
          cn_n = sum(n_true),
          cn_n_signif = sum(Pearson_Pval_CN < 0.05))

@@

ctrp_grid_summary_mut_corr <- wilcox.test(AUC_zscore ~ Mutation_Status_Nonsilent, data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], paired = FALSE)
ctrp_grid_summary_mut_corr_text <- paste0("W = ", formatC(ctrp_grid_summary_mut_corr$statistic, format = "d", big.mark = ","), "\np = ", round(ctrp_grid_summary_mut_corr$p.value, 3))

ctrp_grid_summary_ge_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$RPKM, method = "pearson", use = "complete.obs")
ctrp_grid_summary_ge_corr_text <- paste0("r(", ctrp_grid_summary_ge_corr$parameter, ") = ", round(ctrp_grid_summary_ge_corr$estimate, 2), "\np ", ifelse(round(ctrp_grid_summary_ge_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_ge_corr$p.value, 3))))

ctrp_grid_summary_cn_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$CN, method = "pearson", use = "complete.obs")
ctrp_grid_summary_cn_corr_text <- paste0("r(", ctrp_grid_summary_cn_corr$parameter, ") = ", formatC(ctrp_grid_summary_cn_corr$estimate, digits = 2, format = "f"), "\np ", ifelse(round(ctrp_grid_summary_cn_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_cn_corr$p.value, 3))))

ctrp_grid_summary_mut_plot <- ggplot(data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], aes(y = AUC_zscore, x = Mutation_Status_Nonsilent, fill = Mutation_Status_Nonsilent)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.6) +
  geom_jitter(width = 0.2, shape = 21) +
  scale_fill_manual(values = c("Wildtype" = "lightsteelblue1", "Mutant" = "steelblue4")) +
  annotate(geom = "text", label = ctrp_grid_summary_mut_corr_text, x = 1.5, y = 1.3) +
  guides(fill = FALSE) +
  labs(x = "ERBB2 mutation status", y = "Afatinib AUC (z-score)") +
  geom_segment(aes(x = 1, y = 1.5, xend = 1.1, yend = 1.5), lwd = 0.2) +
  geom_segment(aes(x = 1.9, y = 1.5, xend = 2, yend = 1.5), lwd = 0.2) +
  geom_segment(aes(x = 1, y = 1.5, xend = 1, yend = 1.35), lwd = 0.2) +
  geom_segment(aes(x = 2, y = 1.5, xend = 2, yend = 1.35), lwd = 0.2)
ctrp_grid_summary_mut_plot
